---
title: "project5_g15"
author: "Amey Athaley, Sachin Balakrishnan, George Chen"
date: "April 17, 2020"
output: pdf_document
---

# 1. Show goodness of fits

```{r}
N = 5000
load('queue.Rdata')
library(MASS)
set.seed(1337)

# Gamma
ia = diff(A)
fit.gamma.ia = fitdistr(ia, 'gamma', lower = 0.001)
simdata = qgamma(ppoints(length(ia)), fit.gamma.ia$estimate[1], fit.gamma.ia$estimate[2])
qqplot(simdata,ia)

```
```{r}
# Gamma
fit.gamma.S = fitdistr(S, 'gamma', lower = 0.001)
simdata = qgamma(ppoints(length(S)), fit.gamma.S$estimate[1], fit.gamma.S$estimate[2])
qqplot(simdata,S)

```


```{r}
# Exponential
ia = diff(A)
fit.exp = fitdistr(ia, 'exponential', lower = 0.001)
simdata = qexp(ppoints(length(ia)), fit.exp$estimate[1])
qqplot(simdata,ia)

```
```{r}
fit.exp = fitdistr(S, 'exponential', lower = 0.001)
simdata = qexp(ppoints(length(S)), fit.exp$estimate[1])
qqplot(simdata,S)

```


```{r}
# Weibull
ia = diff(A)
fit.weib = fitdistr(ia, 'weibull', lower = 0.001)
simdata = qweibull(ppoints(length(ia)), fit.weib$estimate[1], fit.weib$estimate[2])
qqplot(simdata,ia)

```
```{r}
# Weibull
fit.weib = fitdistr(S, 'weibull', lower = 0.001)
simdata = qweibull(ppoints(length(S)), fit.weib$estimate[1], fit.weib$estimate[2])
qqplot(simdata,S)
```


Based on our results above, the gamma distribution seems to be the best fit for both inter-arrival time and service time.

# 2. Simulate the queuing system (customers join queues randomly)

```{r}
counters = 20
obj = rep(0,20)

for (ctr in 1:counters) {

T = replicate(ctr, list(0))
D = replicate(ctr, list(0))
W = replicate(ctr, list(0))

choice = sample(1:ctr,N,replace=TRUE)

tau = rgamma(N, fit.gamma.ia$estimate[1], fit.gamma.ia$estimate[2])
S = rgamma(N, fit.gamma.S$estimate[1], fit.gamma.S$estimate[2])

A = c(0,cumsum(tau))
for (i in 1:ctr) {
  T[[i]][1] = 0
  D[[i]][1] = S[match(i,choice)]
  W[[i]][1] = 0
}
for (i in 2:N){
  join = choice[i]
  T[[join]] = append(T[[join]], max(D[[join]][length(D[[join]]-1)],A[i])) 
  D[[join]] = append(D[[join]], T[[join]][length(T[[join]])] + S[i])
  W[[join]] = append(W[[join]],T[[join]][length(T[[join]])] - A[i])
}

ttl.salary = 0
for (i in 1:ctr) {
  ttl.salary = ttl.salary + D[[i]][length(D[[i]])] - A[[i]][1]
}
ttl.salary = ttl.salary * 40/60

cnt.annoyed = 0
for (i in 1:ctr) {
  for (j in W[[i]]) {
    if (j>10) {cnt.annoyed=cnt.annoyed+1}
  }
}

obj[ctr] = ttl.salary + cnt.annoyed
}
```


```{r}
plot(1:counters,obj,type="l",xlab='Open counters',ylab='Expected Cost')
```
```{r}
obj[15]
```

According to our simulation, 15 open counters is the optimal number, and the expected cost is $7314.019 (under the situation when customers randomly join a queue)


# 3. Simulate the queue (all queues combined)

```{r}
counters = 20
obj = rep(0,20)

for (ctr in 1:counters) {

T = replicate(ctr, list(0))
D = replicate(ctr, list(0))
W = replicate(ctr, list(0))

tau = rgamma(N, fit.gamma.ia$estimate[1], fit.gamma.ia$estimate[2])
S = rgamma(N, fit.gamma.S$estimate[1], fit.gamma.S$estimate[2])
A = c(0,cumsum(tau))

for (i in 1:ctr) {
  T[[i]][1] = 0
  D[[i]][1] = S[i]
  W[[i]][1] = 0
}

for (i in (ctr+1):N) {
  earliest.depart = vapply(D,tail,1,FUN.VALUE=numeric(1))
  join = which.min(earliest.depart)
  T[[join]] = append(T[[join]], max(D[[join]][length(D[[join]]-1)],A[i])) 
  D[[join]] = append(D[[join]], T[[join]][length(T[[join]])] + S[i])
  W[[join]] = append(W[[join]],T[[join]][length(T[[join]])] - A[i])
}

ttl.salary = 0
for (i in 1:ctr) {
  ttl.salary = ttl.salary + D[[i]][length(D[[i]])] - A[[i]][1]
}
ttl.salary = ttl.salary * 40/60

cnt.annoyed = 0
for (i in 1:ctr) {
  for (j in W[[i]]) {
    if (j>10) {cnt.annoyed=cnt.annoyed+1}
  }
}

obj[ctr] = ttl.salary + cnt.annoyed

}
```

```{r}
plot(1:counters,obj,type="l",xlab='Open counters',ylab='Expected Cost')
```

```{r}
obj[13]
```

According to our simulation, 13 is the optimal number of the counters, and $5750.829 is the expected cost (under the situation when all queues are combined and customers joins any counter that opens up)